\bf\mftitle

### 2011-03-01 doc/jInfer/autoeditor/autoeditor.tex
3187368 - Review documentation: cleanup - autoeditor done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Mário Mikula \\ \hline
Required tokens       & org.openide.windows.WindowManager \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & Base \\ 
					   & JUNG \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.autoeditor} \\ 
					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer} \\
   					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts} \\
   					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.gui.component} \\ \hline
\end{tabular}

@@

\begin{figure}
\centering\includegraphics[scale=\myscale]{uml_base_classes}
\caption{Class diagram for the base classes.} \label{uml_base_classes}
\end{figure}

@@

Source codes of \code{State\.Picking\.Component} resides in package \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.gui.\.component}, \code{State\-Picking\-Visualizer} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer} and \code{Vertex\-Picking\-Graph\-Mouse\-Plugin} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer.\.graphmouseplugins}.\\

@@

\begin{figure}
\centering\includegraphics[scale=0.6]{screenshot}
\caption{Screenshot of \jmodule{AutoEditor} GUI} \label{figure_gui}
\end{figure}

@@

Source codes of \code{StatesPickingComponent} reside in package \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.gui.\.component}, \code{States\-Picking\-Visualizer} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer} and \code{Vertices\-Picking\-Graph\-Mouse\-Plugin} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer.\.graphmouseplugins}.\\

@@

      StatesPickingComponent<T> panel = new StatesPickingComponent<T>();
      panel.setVisualizer(visualizer);
      if (selectTwo) {
        panel.setLabel("Automaton for element <" + elementName
          + ">. Please select states to be merged and click continue. Select at least 2 states.");
      } else {
        panel.setLabel("Automaton for element <" + elementName
          + ">. Please select states to be merged and click continue.");
      }

@@

All settings provided by \jmodule{AutoEditor} are NetBeans-wide. The options panel along with all the logic is in the \code{cz.cuni.mff.ksi.jinfer.autoeditor.options} package. Available options include setting the color of the background, colors and shapes of some special types of automaton states.\\

To have some effect, these settings need to be implemented by extensions of \code{Visualizer} class. For examples, see source codes of \code{StatePickingVisualizer} and \code{StatesPickingVisualizer} classes.\\

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Mário Mikula \\ \hline
Required tokens       & \code{org.openide.windows.WindowManager} \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & Base \\ 
					   & JUNG \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.autoeditor} \\ 
					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer} \\
   					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts} \\
   					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.gui.component} \\ \hline
\end{tabular}

@@

\begin{figure}
\centering\includegraphics[width=\textwidth]{uml_base_classes}
\caption{Class diagram for the base classes.} \label{uml_base_classes}
\end{figure}

@@

Source codes of \code{State\.Picking\.Component} resides in package \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.gui.\.com\.po\.nent}, \code{State\-Picking\-Visualizer} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer} and \code{Ver\.tex\-Pick\.ing\-Graph\-Mou\.se\-Plug\.in} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer.\.graphmouseplugins}.\\

@@

\begin{figure}
\centering\includegraphics[width=\textwidth]{screenshot}
\caption{Screenshot of \jmodule{AutoEditor} GUI} \label{figure_gui}
\end{figure}

@@

Source codes of \code{StatesPickingComponent} reside in package \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.gui.\.com\.po\.nent}, \code{States\-Picking\-Visualizer} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer} and \code{Vertices\-Picking\-Graph\-Mouse\-Plugin} in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.autoeditor.\.automatonvisualizer.\.graphmouseplugins}.\\

@@

      StatesPickingComponent<T> panel = new StatesPickingComponent<T>();
      panel.setVisualizer(visualizer);
      if (selectTwo) {
        panel.setLabel("Automaton for element <" + elementName
          + ">. Please select states to be merged and click continue."
          + " Select at least 2 states.");
      } else {
        panel.setLabel("Automaton for element <" + elementName
          + ">. Please select states to be merged and click continue.");
      }

@@

All settings provided by \jmodule{AutoEditor} are NetBeans-wide. The options panel along with all the logic is in the \code{cz.cuni.mff.ksi.jinfer.autoeditor.options} package. Available options include setting the color of the background, colors and shapes of some special types of automaton states. \\

To have some effect, these settings need to be implemented by extensions of \code{Visualizer} class. For examples, see source codes of \code{StatePickingVisualizer} and \code{StatesPickingVisualizer} classes.
